Multi-fluids for Representing Sub-filter-scale Convection

### 2020-05-04 submit2/makeFigs/multiFluidBubble_500_1.tex
Nearly ready to resubmit. A better pressure perturbation model is used.

$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=4\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$,

@@

\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer/500/Pcompare}\tabularnewline

@@

$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=6\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$,

@@

\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_6e4_divTransfer/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_6e4_divTransfer/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_6e4_divTransfer/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_6e4_divTransfer/500/Pcompare}\tabularnewline

>>>>

$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=1\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$,

@@

\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer/500/Pcompare}\tabularnewline

@@

$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=4\!\!\times\!\!10^{3}\text{m}^{2}\text{s}^{-1}$,

@@

\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e3_divTransfer/500/Pcompare}\tabularnewline

### 2020-05-04 submit2/makeFigs/multiFluidBubble_500_2.tex
Nearly ready to resubmit. A better pressure perturbation model is used.

$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=4\times10^{4}\text{m}^{2}\text{s}^{-1}$,

@@

\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_drag/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_drag/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_drag/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_drag/500/Pcompare}\tabularnewline

@@

$S_{ij}=0$, \hspace{6pt} $\gamma=4\times10^{4}\text{m}^{2}\text{s}^{-1}$,

@@

\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4/500/Pcompare}\tabularnewline

@@

$S_{ij}=w_{1}0.2/r_{c}$, \hspace{6pt} $\gamma=4\times10^{4}\text{m}^{2}\text{s}^{-1}$,

@@

\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_ent/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_ent/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_ent/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_ent/500/Pcompare}\tabularnewline

@@

\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT0/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT0/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT0/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT0/500/Pcompare}\tabularnewline

@@

\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT05/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT05/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT05/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_4e4_divTransfer_bT05/500/Pcompare}\tabularnewline

>>>>

$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt} $\gamma=1\times10^{4}\text{m}^{2}\text{s}^{-1}$,

@@

\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_drag/500/Pcompare}\tabularnewline

@@

$S_{ij}=0$, \hspace{6pt} $\gamma=1\times10^{4}\text{m}^{2}\text{s}^{-1}$,

@@

\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4/500/Pcompare}\tabularnewline

@@

$S_{ij}=w_{1}0.2/r_{c}$, \hspace{6pt} $\gamma=1\times10^{4}\text{m}^{2}\text{s}^{-1}$,

@@

\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_ent/500/Pcompare}\tabularnewline

@@

\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT0/500/Pcompare}\tabularnewline

@@

\includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/500/sigmaCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/500/bCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/500/wCompare} & \includegraphics[scale=0.6]{/home/hilary/OpenFOAM/hilary-7/run/hilary/warmBubble/Boussinesq/multiFluid/singleColumn_Pi_1e4_divTransfer_bT05/500/Pcompare}\tabularnewline
